%==============================================================================
% Sjabloon onderzoeksvoorstel bachproef
%==============================================================================
% Gebaseerd op document class `hogent-article'
% zie <https://github.com/HoGentTIN/latex-hogent-article>

% Voor een voorstel in het Engels: voeg de documentclass-optie [english] toe.
% Let op: kan enkel na toestemming van de bachelorproefcoördinator!
\documentclass{hogent-article}

% Invoegen bibliografiebestand
\addbibresource{voorstel.bib}

% Informatie over de opleiding, het vak en soort opdracht
%\studyprogramme{Professionele bachelor toegepaste informatica}
%\course{Bachelorproef}
%\assignmenttype{Onderzoeksvoorstel}
% Voor een voorstel in het Engels, haal de volgende 3 regels uit commentaar
\studyprogramme{Bachelor of applied information technology}
\course{Bachelor thesis}
\assignmenttype{Research proposal}

\academicyear{2022-2023} % TODO: pas het academiejaar aan

% TODO: Werktitel
\title{Establishing Best Practices for IaC in an Active Directory Environment: A Proof of Concept (POC) with BitBucket and Stonebranch for Enforcing Code Control, Security Measures, and Automatic Deployment}

% TODO: Studentnaam en emailadres invullen
\author{De Boeck Pieterjan}
\email{pieterjan.deboeck@student.hogent.be}

% TODO: Medestudent
% Gaat het om een bachelorproef in samenwerking met een student in een andere
% opleiding? Geef dan de naam en emailadres hier
% \author{Yasmine Alaoui (naam opleiding)}
% \email{yasmine.alaoui@student.hogent.be}

% TODO: Geef de co-promotor op
\supervisor[Co-promotor]{R.Vyhlídal (K, \href{mailto:richard.vyhlidal@kbc.com}{richard.vyhlidal@kbc.com})}

% Binnen welke specialisatierichting uit 3TI situeert dit onderzoek zich?
% Kies uit deze lijst:
%
% - Mobile \& Enterprise development
% - AI \& Data Engineering
% - Functional \& Business Analysis
% - System \& Network Administrator
% - Mainframe Expert
% - Als het onderzoek niet past binnen een van deze domeinen specifieer je deze
%   zelf
%
\specialisation{System \& Network Administrator}
\keywords{IaC, BitBucket, Stonebranch}

\begin{document}

\begin{abstract}
  A team from KBC working in the active directory sector of KBC needs to research an IaC environment to automate the management of their code. The need for such environments are high and in a company like KBC security is a big part of it. This research proposal aims to investigate and establish the best practices for such an environment. After the research, I would like to establish a proof of concept leveraging BitBucket for version control and Stonebranch for orchestrating code deployment. This on request of KBC.
  The Primary objectives of this research include:
  Code Control: Evaluate how BitBucket is a as a version control system. Research the tools that can be used with it. Assess the capabilities of BitBucket in handling code collaboration, versioning, and change tracking in a multi-team, enterprise environment.
  Security measures: Investigate the security considerations around BitBucket and IaC. Adress Issues like access control and encryption between the active directory, IaC tools, and BitBucket
  Automatic deployment: Explore the automation capabilities of StoneBranch and how it would integrate with BitBucket. 
  The methodology of this research will involve making a proof of concept environment that will include all of the primary objectives preferably with “Best practices” implemented.
  The expected outcome of this research is a working POC implementation that KBC could use as reference for setting up their own environment
  \end{abstract}

\tableofcontents

% De hoofdtekst van het voorstel zit in een apart bestand, zodat het makkelijk
% kan opgenomen worden in de bijlagen van de bachelorproef zelf.
\input{voorstel-inhoud}

\printbibliography[heading=bibintoc]

\end{document}